---
title: "Lab 00 - Hello IDS!"
author: "Chunlin Chen"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Eric", "Fiona", "Amy", 
           "Iris", "Ryan"),
  github_username = c("whatever89", "disneyland01", "chunlina312", 
                      "nemo555", "blackhole47"), 
  colour = c("violet", "blue", "yellow", 
             "green", "red"),
  hobby = c("cooking", "sleeping", "tennis", 
            "hiking", "skating"),
  favourite_number = c(8, 5, 7, 9, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

The bar plot shows the favourite numbers of team members against their GitHub usernames. Each bar represents a team member's GitHub username on the x-axis and their favourite number on the y-axis, filled with their chosen favourite colour.

